---
title: "simpleRegress"
author: "Mallori Rojas"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```
for model length~neck, adjusted r^2 = 0.75

## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

## length based on age

```{r}
ageModel <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(ageModel)
summary.lm(ageModel)
```

adjusted $r^2$ for th age model is 0.51, this is less than the adjusted $r^2$ for neck, so this model is not as good as the neck model.

```{r}
chestModel <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(chestModel)
summary.lm(chestModel)
```

adjusted $r^2$ for the chest model is , this is less than the adjusted $r^2$ for length, so this model is not as good as the chest model.


```{r}
sexModel <- lm(LENGTH~SEX,data=bears)
plot(LENGTH~SEX,data=bears)
abline(sexModel)
summary.lm(sexModel)
```


bla bla


```{r}
headlenModel <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(headlenModel)
summary.lm(headlenModel)
```

bla bla


```{r}
weightModel <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(weightModel)
summary.lm(weightModel)
```


bla bla


```{r}
headwthModel <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(headwthModel)
summary.lm(headwthModel)
```

BLA BLA
